%!TEX root = ../main.tex
\section{Introduction}
\label{sec:introduction}
2020 was a challenging year from many perspectives especially because of the COVID19
pandemic.  As a study from Cambridge shows conspiracy theories about this topic are rising
everywhere \citep{freeman_waite_etal_2020}. These theories can be  dangerous, as one can
conduct from the Capitol riot in the United States January 6th, 2021. At this event,
people believed in a conspiracy theory that Trump's victory in the US elections 2020 was 
stolen from him and tried therefore to ``take it back'' by storming the US
Capitol~\citep{williamson_2021}. They organized this riot on a social media platform. The 
question is: How can we fight conspiracies like that? A first step could be to try to 
understand how conspiracy theories work in the context of social media.  Why do certain
theories get shared? With the help of Natural Language Processing (NLP) and machine
learning we analyzed posts written by conspiracy  theorists in order to find answers  to
the following questions: can we predict the impact of a conspiracy theory post using the 
post's content? How do we define impact? Can we give an explanation on what makes a post 
successful or unsuccessful among conspiracy theorist? While NLP and neural networks can be
used to process text and assign a label to it, often it is to hard for humans to
understand how they came to a certain conclusion. The field of eXplainable Artificial 
Intelligence (XAI) tries to give explanations about why machine learning models make a 
specific prediction.  If we only have a model which predicts the impact of a social media
post, we still do not  know how the model came to this decision. With XAI we can reason
about it - or more  importantly: we can reason about what a successful post might look
like and thus identify what stances conspiracy theorists support. 

% Edo: global XAI could be used to understand social groups and posts impact within those groups. So you reviewed global XAI methods, you tried to predict posts impact on crowdtangle, and future work should focus on the combination if they find good data that is predictable
% \begin{itemize}
%     \item Similar to the extended abstract
%     \item Introduction to the topic of XAI 
%     \item General methodology
% \end{itemize}